### 2019-09-25 liability.tex
updates liability

\subsection{Hotels}
The Marriott, Hampton, Illini Union, and I Hotel are not responsible for lost, stolen, or damaged items. Damages to their premise will be charged to those responsible. These terms are to be agreed upon contractually on a guest by guest basis as rooms become occupied. Hotels are covered through their own insurance policies.

@@

\subsection{Dining}
University Catering, and Round Barn assume all liability regarding foodborne illness derived from their respective events.

>>>>

\subsection{Hotels}
The Illini Union and the Garden Hotel in Urbana (soon to be the Radisson) are not responsible for lost, stolen, or damaged items. Damages to their premise will be charged to those responsible. These terms are to be agreed upon contractually on a guest by guest basis as rooms become occupied. Hotels are covered through their own insurance policies.

@@

\subsection{Dining}
University Catering, Round Barn, and the Garden Hotel in Urbana (soon to be the Radisson) assume all liability regarding foodborne illness derived from their respective events.
